---
title: "Get started with dymium"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}

```

# Pre-requisitons

It is recommended that you use RStudio as your R [IDE](https://en.wikipedia.org/wiki/Integrated_development_environment) which can be downloaded for free from [this link](www.rstudio.com/download).


# Installation

This tutorial is a quick start guide to build your first microsimulation model pipeline with `dymium`. 

We begin by install the dymium package using either the `devtools` package or the `remotes` package.

```{r eval = FALSE}
# the lines below install the `remotes` package if it is not already installed.
if (!require("remotes")) {
  install.packages("remotes")  
}

# this install the `dymium` package from its github repo.
remotes::install_github("dymium-org/dymium")
```

By install the `dymium` package it will automatically install other dymium packages such as `dymiumCore` and `dymiumApp` as part of its dependencies. Basically, the `dymium` package act as a master package that when it is loaded it loads all other dymium packages, like the `tidyverse` package.

# First model

**Make sure you have completed the installation steps in the previous section.**

To create your first dymium model you must first prepare your microdata which is the data of your agents.`dymiumCore` provides a toy dataset which contains linkable records of individuals and households with some basic attributes and relationship variables. But first you must load the package into your active R environment.

```{r}
library(dymium)
```
